`flippant` --- An `R` package for the automated analysis of fluorescense--based

### 2016-09-11 inst/manuscript/manuscript.rmd
Fix a "Declariations" section according to BMC Bioinformatic's requirements;

# Acknowledgements
J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medicine -- Qatar, a program 
funded by Qatar Foundation. This study was made possible by NPRP grant
5--669--1--112 from the Qatar National Research Fund (a member of Qatar 
Foundation). The statements made herein are solely the responsibility of the
authors. B.P. was also supported by the Austrian Science Fund (FWF), project
J3686--B21.

>>>>

# Declarations
## Ethics approval and consent to participate
Not applicable.

## Consent for publication
Not applicable.

## Availability of data and material
Upon acceptance of the manuscript, `flippant` will be depositied as a
self--contained `R` package including all data presented in the `Bioconductor`
collection of tools for biomedical data analysis [@huber_orchestrating_2015].

## Competing interests
The authors declare that they have no competing interests.

## Funding
J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
Research Program'' funds at Weill Cornell Medicine -- Qatar, a program 
funded by Qatar Foundation. This study was made possible by NPRP grant
5--669--1--112 from the Qatar National Research Fund (a member of Qatar 
Foundation). The statements made herein are solely the responsibility of the
authors. B.P. was also supported by the Austrian Science Fund (FWF), project
J3686--B21.

## Authors' contributions
R.J.C and J.G. wrote the code, B.P., M.A.G. and A.K.M. guided the implementation
and edited the manuscript, which J.G. wrote. B.P. provided the exemplary assay
data. A.K.M. and J.G. supervised the work.
